\documentclass{tccv}

\makeatletter
\DeclareOldFontCommand{\rm}{\normalfont\rmfamily}{\mathrm}
\DeclareOldFontCommand{\sf}{\normalfont\sffamily}{\mathsf}
\DeclareOldFontCommand{\tt}{\normalfont\ttfamily}{\mathtt}
\DeclareOldFontCommand{\bf}{\normalfont\bfseries}{\mathbf}
\DeclareOldFontCommand{\it}{\normalfont\itshape}{\mathit}
\DeclareOldFontCommand{\sl}{\normalfont\slshape}{\@nomath\sl}
\DeclareOldFontCommand{\sc}{\normalfont\scshape}{\@nomath\sc}
\makeatother

\usepackage[brazil]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

\begin{document}

\part{Manoel de Albuquerque Lira Amaro}

\section{Work experience}

\begin{eventlist}

\item{2017 -- present}
     {Journi GmbH.}
     {Software Engineer}

Android App (Java and Kotlin) and Backend development using Scala, PostgreSQL, React.JS and DevOps (Docker, AWS EB, RDS).

\item{2016 -- 2018}
     {Channel (H) Inc.}
     {Software Engineer}

Software development using Ruby on Rails for US Health Care related business, including parsing of multiple and differents EMRs' data and delivering summarized information to patients and clinicians.

\item{2013 -- 2016}
     {Phoebus Tecnologia}
     {Software Engineer}

Software development for financial transaction processing using Java for the transaction server and web development with Java, Flex and Angular JS (migration from Flex to Angular JS). Also development of Android applications for financial transactions.

\item{2012 -- 2013}
     {Inovecinco Tecnologia}
     {Internship and Software Engineer}

Software development of web sites and systems using Ruby on Rails as main technology, and performed the migration of the entire system from Java to Ruby on Rails.

\item{2010 -- 2013}
     {LAViD - Advanced Audio and Video Laboratory}
     {Researcher}

Research and development of \href{http://knowledgetv.lavid.ufpb.br/}{Knowledge TV} project,
focusing on the Web Services and computacional agents for the Semantic Query service, using Linked Data and Semantic Web principles.

\item{2009 -- 2010}
     {eGen Group}
     {Internship}

Software development of web and ERP (Enterprise Resource Planning) systems with Java as main technology and some web frameworks, like JSF and Struts.

\end{eventlist}

\personal
    [manoamaro.github.io]
    {Vienna, Austria}
    {+43 0677 6248-0117}
    {manoel.al.amaro@gmail.com}

\section{Education}

\begin{yearlist}

\item{2011 -- 2014}
     {Master in Computer Science}
     {UFPB Paraiba, Brazil}

\item[Systems Development Technologies]{2008 -- 2011}
     {Informatic technologist}
     {IFPB Paraiba, Brazil}

\end{yearlist}

\section{Public projects}

\begin{yearlist}

\item{Present}
     {Github Projects (\href{https://github.com/manoamaro}{github})}
     {Various home and college projects}

\item{2017}
     {Channel(H) Golion}
     {Channel(H) technology is used to supply personalized data to a wide array of medical applications}

\item{2016}
     {Rede Criança PB}
     {System to manage and publish information of public institutions that supports children and families}

\end{yearlist}

\section{Communication skills}

\begin{factlist}
\item{Portuguese}{Native speaker}
\item{English}{Fluent}
\item{German}{Begginer}
\end{factlist}

\section{Software skills}

\begin{factlist}

\item{Good level}
     {Java, Scala, Ruby on Rails, Frontend (react.js), git, Android (Java, Kotlin), DevOps(Linux, Docker, AWS, Kubernetes), Node JS}

\item{Intermediate}
     {iOS Development, GoLang}

\end{factlist}

\end{document}
